\documentclass{beamer}

\usepackage{verbatim}

\usetheme{Warsaw}

\title{Chirpy!}
\begin{document}

\begin{frame}
    \maketitle
\end{frame}

\begin{frame}
    \frametitle{What is it?}
    A cryptographic chat application that:
    \begin{itemize}
        \item 
            uses sensors to generate entropy.
        \item
            uses Twitter to host the ciphertext.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{State of Android/Linux Random}
    \begin{itemize}
        \item 
            \texttt{SecureRandom} is a psuedo random number generator that is seeded
            at boot
        \item
            /dev/random and /dev/urandom are psuedo random number generator
            gathering entropy from keyboard timings, mouse timings, etc.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Our Idea}
    \begin{itemize}
        \item
            Android devices have sensors!
        \item
            We worked with accelerometer
    \end{itemize}
\end{frame} 

\begin{frame}
    \frametitle{State of ``Twitter Chats''}
    \begin{itemize}
        \item
            Twitter is of the most reliable and public ways to post messages.
        \item
            It has been used to mobilize people during unrest.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Our Idea}
    \begin{itemize}
        \item 
            Some messages should be private!
        \item
            We facilitate posting ciphertext to Twitter
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Future Work}
    \begin{itemize}
        \item 
            Implement a more practical cryptographic scheme.
        \item
            More control over saving (or not!) messages.
    \end{itemize}
    
\end{frame}

\end{document}
